`r glue::glue('inferCNV results for {params$library_id} with {params$reference_name} reference')`

### 2025-05-14 analyses/infercnv-consensus-cell-type/template-notebooks/SCPCP000015_explore-infercnv-results.Rmd
update text based on reference type

```{r, results = 'asis'}
ref_text <- list(
  "ref_endo" = "endothelial",
  "ref_immune" = "immune",
  "ref_endo-immune" = "endothelial and immune"
)
glue::glue(
  "`inferCNV` was run with the following normal reference: `{params$reference_name}`.
  This reference contains all {ref_text[[params$reference_name]]}  cells across `SCPCP000015` libraries, excluding any which were also identified as tumor in the `cell-type-ewings` analysis module.
  "
)
```

>>>>

```{r, results = 'asis'}
ref_text <- list(
  "ref_endo" = "endothelial",
  "ref_immune" = "immune",
  "ref_endo-immune" = "endothelial and immune"
)
if (stringr::str_detect(opts$reference_name, "internal")) {
  reference_type_text <- glue::glue("within the `SCPCL000822` library")
} else {
  reference_type_text <- glue::glue("across all `SCPCP000015` libraries")
}

glue::glue(
  "`inferCNV` was run with the following normal reference: `{params$reference_name}`.
  This reference contains all {ref_text[[params$reference_name]]} cells {reference_type_text}, excluding any which were also identified as tumor in the `cell-type-ewings` analysis module.
  "
)
```
